Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-09-11 tex/scam/optimization.tex
minor edits

\begin{remark}
  In our sparsistency analysis, we assume that an upper bound $B$ to
  $\| f^*_k \|_\infty$ is known, and that we constrain our estimate
  $\hat{f}$ to obey the same boundedness condition.  That is, for each
  $k$, we require that $\|\hat{f}_k\|_\infty \leq B$. This boundedness
  constraint can be easily added to our optimization program. In
  optimization~\eqref{opt:alternate_opt}, we can enforce the boundedness
  condition by adding $p$ constraints $\| \bar{\Delta}_k d_k
  \|_\infty \leq B$ for $k=1,\ldots,p$ (and similarly for
  optimization~\eqref{opt:alternate_opt_concave}). We emphasize that we
  use the boundedness constraint only in our theoretical analysis; 
  our experiments do not impose any such condition.
\end{remark}

>>>>

\begin{remark}
  In our analysis, we assume that an upper bound $B$ to
  $\| f^*_k \|_\infty$ is known, and that we constrain our estimate
  $\hat{f}$ to obey the same boundedness condition.  That is, for each
  $k$, we require that $\|\hat{f}_k\|_\infty \leq B$. This boundedness
  constraint can be easily added to our optimization program. In
  optimization~\eqref{opt:alternate_opt}, we can enforce the boundedness
  condition by adding $p$ constraints $\| \bar{\Delta}_k d_k
  \|_\infty \leq B$ for $k=1,\ldots,p$ (and similarly for
  optimization~\eqref{opt:alternate_opt_concave}). We emphasize that we
  use the boundedness constraint only in our theoretical analysis; 
  our experiments do not impose any such condition.
\end{remark}
